A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2022-11-25 pilot-publication/manuscript.Rmd
Work on results

---
## compile with:
## Rscript -e "rmarkdown::render('manuscript-clean.Rmd', output_format = 'all')"
title: A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes  
author: Trauma life support training Effectiveness Research Network (TERN) collaborators
bibliography: bibliography.bib
csl: nature.csl
output:
    bookdown::word_document2:
      toc: false
      number_sections: false
      reference_docx: "reference.docx"
    md_document: default
---

@@

Between `r start.date` and `r end.date`, we enrolled `r n.patients`
trauma patients from `r n.centres` participating centres. The ATLS arm
enrolled `r n.atls` patients, the PTC arm `r n.ptc` patients, and the
standard care arm `r n.control` patients. The study flowchart is shown
in Figure X and sample characteristics across trial arms are shown in
Table X. Overall, the number of females were X (X%), the median age
was X (IQR X), and the median ISS was X (IQR X). A total of X (X%)
patients had the primary outcome of mortality at 30 days after arrival
to the emergency department.

>>>>

---
## compile with:
## Rscript -e "rmarkdown::render('manuscript.Rmd', output_format = 'all')"
title: A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes  
author: Trauma life support training Effectiveness Research Network (TERN) collaborators
bibliography: bibliography.bib
csl: nature.csl
output:
    bookdown::word_document2:
      toc: false
      number_sections: false
      reference_docx: "reference.docx"
    md_document: default
---

@@

Between `r start.date` and `r end.date`, we enrolled `r n.patients`
trauma patients from `r n.centres` participating centres. The ATLS arm
enrolled `r n.atls` patients, the PTC arm `r n.ptc` patients, and the
standard care arm `r n.control` patients. We trained a total of 
`r n.residents` residents, `r n.atls.residents` in ATLS, and 
`r n.ptc.residents` in PTC.

The study flowchart is shown in Figure X and patient sample
characteristics across trial arms are shown in Table X. Overall, the
number of females were X (X%), the median age was X (IQR X), and the
median ISS was X (IQR X). A total of X (X%) patients had the primary
outcome of mortality at 30 days after arrival to the emergency
department.
